---
output: rmarkdown::github_document
---

# webhose

Tools to Work with the 'webhose.io' 'API'

## Description

The 'webhose.io' <https://webhose.io/about> 'API' provides access to structured 
web data feeds across vertical content domains. Their crawlers download the web, 
structure the data and index save it into domain-specific repositories that can be
accessed on demand. Methods are provided to query and retrieve content from this 'API'.

## TODO

Cover the rest of the wehbose.io API. 

Covered are 

* the [News/Blog/Discussions API](https://docs.webhose.io/docs/newsblogsdiscussions-api)
* the [Reviews API](https://docs.webhose.io/v1.0/docs/reviews-api)
* the [Products API](https://docs.webhose.io/v1.0/docs/ecommerce-product-data-api)

## What's in the tin?

The following functions are implemented:

* `filter_posts`:	Retrieve structured posts data from news articles, blog posts and online discussions
* `fetch_posts`: Fetch all structured posts data from news articles, blog posts and online discussions
*  `filter_reviews`: Retrieve structured reviews data from hundreds of review sites
* `fetch_reviews`: Fetch all structured reviews data from hundreds of review sites
* `filter_prodcuts`: Retrieve structured products data from thousands of online retailers and e-commerce sites
* `fetch_products`: Fetch all structured products data from thousands of online retailers and e-commerce sites

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/webhose")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(webhose)

# current verison
packageVersion("webhose")
```

Make just one call and/or handle API pagination on your own:

```{r message=FALSE, warning=FALSE, error=FALSE}
res <- filter_posts("(China AND United) language:english site_type:news site:bloomberg.com", ts = 1213456)

str(res)
```

Auto-handle pagination (NOTE: you're more likelky to rip through your plan API credits this way):

```{r message=FALSE, warning=FALSE, error=FALSE}
res <- fetch_posts("(China AND United) language:english site_type:news site:bloomberg.com",ts = 1213456)

dplyr::glimpse(res)
```
